---
title: "BLBLM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{blblm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(blblm)
```

## BLB (Bag of Little Bootstraps)

The Bag of Little Bootstraps algorithm was created as a method of estimating underlying sampling parameters, without the time loss provided by the classical Bootstrap method. In this method, we utilize a computer's ability to multitask by running a classical Bootstrap on multiple sub-samples of our original dataset, oftentimes in parallel. 

This method returns very similar results to the classical method - but with a significant time save. This makes it an ultimately better option for large, computationally-heavy estimations.

-----------

## Linear Modeling

Linear Regression is the method of attemping to find a meaningful linear relationship between different variables of data. 

The method of linear modeling used in this package is via the "stats" package. We first reshape the data to our formula, using the method "model.frame"

```{r, include = FALSE}
x = rnorm(5)
y = rnorm(5)

data = data.frame(x = x, y = y)
formula = y ~ x
environment(formula) <- environment()
```




```{r}
data
m <- model.frame(formula, data)
m
```

The model.frame function reorders the data to prepare it for regression.

Next, we create a matrix X to solve y = mX + b using linear algebra. 
```{r}
X <- model.matrix(formula, m)
X
```

Lastly, we create a variable y to solve for (our response variable). This becomes a horizontal vector, so that we can solve using using matrix multiplication.
```{r}
y <- model.response(m)
y
```
Lastly, we use a multinomial distribution to compute the regression using *lm_wfit* from the *stats* package.

_______________

## Bag of Little Bootstraps Linear Modeling (BLBLM)

Our function blblm() applies the Bag of Little Bootstraps algorithm to compute multiple linear regression estimates, then the various package methods allow us to combine results and create confidence intervals. 

We take five parameters in our function:

* *Formula*
    + The desired formula for the regression estimate\
    
* *Data*
    + The dataset to be regressed\  
    
* *m*
    + The desired number of subsamples to be created
    + (Default - 10)\  
    
* *B*
    + The desired number of samples to be taken for each of the Bootstraps
    + (Default - 5000)\  
    
* *Parallel*
    + Enter TRUE if utilizing all available cores is desired, or FALSE for using a single core
    + (Default - FALSE)\  
    
    
The function then splits the data into *m* subsections, and performs a bootstrapped linear regression on each of the samples. 

______________-

## Return Value

The function returns a blblm object with two parts: the formula and the estimates. These can be accessed by R's $ notation.

The *estimates* returns a list of lists - the outer list is of length *m* and each inner list is of length *B* with both the estimated coefficients of regression and the sigma value.

## Methods

The package contains five methods:

* *Print*
    + Calling print() on a blblm object will print the formula given in the function call.\  
    
* *Sigma*
    + Returns the mean of all the estimated sigma values.
    + Has an optional parameter *confidence* that will also return a confidence interval for the value. \  
    
* *Coef*
    + Returns the mean of all the estimated coefficient values.
    + Has an optional parameter *confidence* that will also return a confidence interval for the value. \  
    
* *Confint* 
    + Returns a confidence interval for the given parameter estimation. \  
    
* *Predict*
    + Returns a predicted value for the given parameter, given a parameter value.
    + Has an optional parameter *confidence* that will also return a confidence interval for the value. \  
    